\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-27 popl-2019-journal-v/paper.tex
Some more comments.
[POPLjv] Update terminology for regions to spatial, shadow, and shared

@@

\section{Introduction}
\label{sec:introduction}
\todo[inline]{TODOS ENABLED!!!}
\todo[inline]{Lau: for camera ready version update reference to technical report (and upload the technical report).}
Secure compilation is an active topic of research (e.g.~\citep{devriese_modular_2017,patrignani_hyper_2017,Abate:2018:GCG:3243734.3243745,new_universal_embedding_2016,juglaret_beyond_2016}), but a real secure compiler is yet to be built.
Secure compilers preserve source-language (security-relevant) properties even when the compiled code interacts with arbitrary target-language components.
Generally, properties that hold in the source language but not in the target language need to be somehow enforced by the compiler.
Two properties that hold in many high-level source languages are well-bracketed control flow and encapsulation of local state, but they are not enforced after compilation to assembly.

@@

The fact that our full abstraction result only applies to reasonable components (see Section~\ref{sec:form-secur-with}) makes it related to full abstraction results for unsafe languages.
In their study of compartmentalization primitives, \Citet{juglaret_beyond_2016} discuss the property of Secure Compartmentalizing Compilation (SCC): a variant of full abstraction that applies to unsafe source languages.
Essentially, they modify standard full abstraction so that preservation and reflection of contextual equivalence are only guaranteed for components that are {\itshape fully defined}, which means essentially that they do not exhibit undefined behavior in any fully defined context.
In follow-up work, \citet{Abate:2018:GCG:3243734.3243745} extend this approach to scenarios where components only start to exhibit undefined behavior after a number of well-defined steps. 
If we see reasonable behavior as defined behavior, then our full abstraction result can be seen as an application of this same idea.
Our results do not apply to dynamic compromise scenarios because they are intended to be used in the verification of a secure compiler where these scenarios are not relevant.

% TODO Relate full-abstraction to other notions of secure compilation

% TODO Relate to Stelios' CSF 2019 paper

>>>>

\renewcommand{\spatialo}{\mathrm{spatial}}
\renewcommand{\spatial}{\mathrm{shadow}}
\renewcommand{\pure}{\mathrm{shared}}

\renewcommand{\purePart}[1]{\plainfun{sharedPart}{#1}}

@@

\renewcommand\lau[1]{{\color{purple} \sf \footnotesize {LS: #1}}\\}
\renewcommand\dominique[1]{{\color{purple} \sf \footnotesize {DD: #1}}\\}
\renewcommand\lars[1]{{\color{purple} \sf \footnotesize {LB: #1}}\\}

\section{Introduction}
\label{sec:introduction}
\todo[inline]{TODOS ENABLED!!!}
\todo[inline]{Lau: for camera ready version update reference to technical report (and upload the technical report).}
Secure compilation is an active topic of research (e.g.~\citep{devriese_modular_2017,patrignani_hyper_2017,Abate:2018:GCG:3243734.3243745,new_universal_embedding_2016,juglaret_beyond_2016}), but a real secure compiler is yet to be built.
\dominique{Reference Patrignani, Ahmed and Clarke's survey paper?}
Secure compilers preserve source-language (security-relevant) properties even when the compiled code interacts with arbitrary target-language components.
Generally, properties that hold in the source language but not in the target language need to be somehow enforced by the compiler.
Two properties that hold in many high-level source languages are well-bracketed control flow and encapsulation of local state, but they are not enforced after compilation to assembly.

@@

The fact that our full abstraction result only applies to reasonable components (see Section~\ref{sec:form-secur-with}) makes it related to full abstraction results for unsafe languages.
In their study of compartmentalization primitives, \Citet{juglaret_beyond_2016} discuss the property of Secure Compartmentalizing Compilation (SCC): a variant of full abstraction that applies to unsafe source languages.
Essentially, they modify standard full abstraction so that preservation and reflection of contextual equivalence are only guaranteed for components that are {\itshape fully defined}, which means essentially that they do not exhibit undefined behavior in any fully defined context.
In follow-up work, \citet{Abate:2018:GCG:3243734.3243745} extend this approach to scenarios where components only start to exhibit undefined behavior after a number of well-defined steps. 
If we see reasonable behavior as defined behavior, then our full abstraction result can be seen as an application of this same idea.
Our results do not apply to dynamic compromise scenarios because they are
intended to be used in the verification of a secure compiler where these
scenarios are not relevant.
\dominique{Perhaps worth pointing out that (I suspect that) our step-bounded reasonability and FTLR, actually does apply in dynamic compromise scenario's. The idea would be to use the theorem multiple times with different step bounds and a different boundary between trusted and untrusted code.
  More concretely, if a component A starts behaving non-reasonable after 10 steps, then first apply the FTLR with n = 9 and component A trusted.
  Then apply the FTLR again with n > 10 and component A no longer trusted.
  Then you get stronger well-bracketedness guarantees until n=9 and weaker ones after that.
  This is a step-bounded version of the idea explained in \cite{patrignani_modular_2016}.}

\dominique{Relate full-abstraction to other notions of secure compilation}

\dominique{Relate to Stelios' CSF 2019 paper}

\dominique{Relate to Thomas Van Strydonck's ICFP19 paper which uses linear capabilities (at a higher level) to enforce separation logic in a fully abstract way.}
